---
title       : "Developing Data Product"
subtitle    : "Shiny App Presentation : Iris Dataset"
author      : "Ritika Pandey"
job         : "Student"
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This presentation is part of the Course Project for the Coursera Developing Data Products class. The peer assessed assignment has two parts. First, we need to create a Shiny application and deploy it on Rstudio's servers. Second, we should use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application. This presentation adresses the second part of the course project.

The app developed for the first part of the assignment is avalilable at:
https://rit2410.shinyapps.io/appshiny/

Source code for ui.R and server.R files are available on the GitHub:

https://github.com/rit2410/Developing-Data-Products




---

## Embedded Code

```{r}
summary(iris)
```

---

```{r}
library(ggplot2)
ggplot(iris,aes(Sepal.Width,(Sepal.Length),color=Species))+
  geom_point(position="jitter")
```

---

## URLs 

For the app : https://rit2410.shinyapps.io/appshiny/

For server and ui codes : https://github.com/rit2410/Developing-Data-Products

---





